The problem and promise of scale in multilayer networks

### 2020-02-03 paper/manuscript.Rmd
fig2 caption v2

---
title: The problem and promise of scale in multilayer networks
author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
output:
  #github_document
   bookdown::pdf_document2
  # bookdown::word_document2:
  #   reference_docx: template.docx
bibliography: ../references/knitcite.bib
---

@@

### Network metrics
We used a series of metrics to characterize the multilayer networks focusing on the relevance of individual layers, 
similarity of layers and the role of individuals. We calculated multidegree, the sum of degree centrality across layers, and neighbourhood, the sum of unique neighbours to each individual [@Berlingerio_2012; @Kivela_2014]. Comparing the multidegree and number of unique neighbours, we measured the connective redundancy, the proportion of neighbours repeated in multiple layers, and the layer relevance, the proportion of neighbours present compared to the neighbourhood for each individual. To measure the role of individuals, we calculated the graph strength for each individual for each layer specific season and landcover context.

e focused on four aspects
of the network: “interlayer correlation and reducibility”
(i.e., correlation between layers and similarities regarding
the information contained in each one; “node versatility”
(i.e., role of each node in the connectedness and information
flow of the network); “community structure” (i.e., whether
there are subsets of nodes more tightly connected among
each other than with the rest); and “motif analysis” (i.e.,
non-random patterns of interconnection between triads).

Node based

Calculated for each layer 
and for multilayer total

For each multilayer network, we calculated a series of metrics on individual layers and  four metrics. These included:
multidegree, graph strength, redundancy/relevance, and  layer similarity.

<!-- GOING
TO NEED MORE HERE (SEE SMITH-AGUILAR ET AL 2019 PAPER FOR REFERENCE ON
EXPLAINING THESE).
-->

<!-- 
ALR: Reference for extending degree centrality to multilayer, neighbors,
connective redundancy and relevance: Berlingerio 2011 "Foundations of
multidimensional..."
-->

* Multidegree
* Degree centrality
* Multidegree
* Degree deviation: standard deviation of degree across layers
* Neighbors/neighborhood (number of unique actors directly connected to each focal): Neighbors = degree within a network layer. But across a multilayer network with multiple layers, some neighbors are repeated. 
* Graph strength
* Connective redundancy: 1 - (neighborhood / degree) When connective redundancy is 0, all edges on all layers are necessary to preserve the social ties
* Relevance: neighborhood of specific layer  / neighbourhood of full ml net. This is the proportion of neighbors present on the layer of focus. Comparing across, it tells you which layers are most important for each individual. 
* layer similarity

* Multidegree: sum of degree across layers. High multidegree = connected to many
individuals across layers. Low multidegree = not connected to many individuals
across layers.

## Varying scale in multilayer networks

### Social scale

@@

(ref:lcres) Variation in multilayer network metrics as a function of changes in landcover resolution, a metric which we interpret as spatial scale. For each landcover resolution (10m, 100m, 250m, 500m and 1000m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter), and four network metrics were calculated. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m. Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10m landcover resolution. B) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution. C) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions. D) Mean graph strength of individuals was weaker during the summer compared to the winter months.

@@

>>>>

---
title: The problem and promise of scale in multilayer networks
author: Alec L. Robitaille^1^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: ^1^Department of Biology, Memorial University of Newfoundland, Canada; ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland
output:
  github_document
  # bookdown::pdf_document2:
  #   number_sections: false
  # bookdown::word_document2:
  #   reference_docx: template.docx
bibliography: ../references/knitcite.bib
---

@@

### Network metrics
We used a series of metrics to characterize the multilayer networks focusing on
the relevance of individual layers, similarity of layers and the role of
individuals. We calculated multidegree, the sum of degree centrality across
layers, and neighbourhood, the sum of unique neighbours to each individual
[@Berlingerio_2012; @Kivela_2014]. Comparing the multidegree and number of
unique neighbours, we measured the connective redundancy, the proportion of
neighbours repeated in multiple layers, and the layer relevance, the proportion
of neighbours present compared to the neighbourhood for each individual
[@Berlingerio_2012]. To measure the role of individuals, we calculated the graph
strength for each individual for each layer specific season and landcover
context <!-- citation?-->. Finally, we calculated the similarity of layers
between seasons, across landcover classes (e.g.: winter open compared to summer
open) using the Pearson correlation coefficient [@Br_dka_2018].

## Varying scale in multilayer networks
### Social scale

@@

@@

(ref:lcres) Variation in multilayer network metrics as a function of changes in landcover resolution, a metric which we interpret as spatial scale. For each landcover resolution (10m, 100m, 250m, 500m and 1000m), multilayer networks were constructed for each landcover class (forest, lichen and open) across two seasons (summer and winter), and four network metrics were calculated and we examined how network metrics changed as a function of changes in spatial scale. A) Similarity of landcover network layers between seasons (e.g.: open summer compared to open winter) showed different responses to changing landcover scale with an increase in similarity for forest layers at 250m and decrease in similarity for open layers at 250m. Note that lichen layer similarity is not shown because individuals did not interact in lichen habitats greater greater than 10m landcover resolution. B) Mean connective redundancy across individuals showed a decreasing trend with increasing landcover resolution. C) Mean layer relevance showed sparse connectivity in summer compared to winter networks and a decrease in winter lichen layer relevance at higher landcover resolutions. D) Mean graph strength of individuals was weaker during the summer compared to the winter months.
